Investigation of Multi-Angle Detection Schemes for Light Scattering of Optically Trapped Asymmetric Colloidal Particles

### 2024-06-07 Latex_files/Manuscripts Scattering/Manuscript_Spie.tex

\documentclass[12pt]{optica-article}

\usepackage{csvsimple}
\usepackage{lineno}

\usepackage{amsmath}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{wrapfig}
\usepackage{geometry}
\usepackage{fancyref}
\usepackage{lineno}
\usepackage{color}
\usepackage{nomencl}
\usepackage{tabularx}
\makenomenclature
\renewcommand{\nomlabel}[1]{\hfil #1\hfil}
\linenumbers

\journal{opticajournal}

\begin{document}

@@

\author{Daniel Maciver, \authormark{1,*}, Praveen Parthasarathi, \authormark{1}, Leo Lue, \authormark{1}, Jan Sefcik, \authormark{1},
Mark Haw, \authormark{1}}

\address{\authormark{1}Department of Chemical Engineering,
	University of Strathclyde, 75 Montrose Street, Glasgow,
	G1 1XL, Scotland}
\email{\authormark{*}daniel.maciver.2016@uni.strath.ac.uk}

\begin{abstract}
  % \justifying
  %
  Optical trapping is a well understood method for transduction and detection
  of forces on trapped colloidal particles, these trapped entities can be
  further characterised using light-scattering, posing a two-fold challenge:
  one experimental, concerning the optimal arrangement of detectors to gather
  data and minimise signal noise, and the other theoretical, involving solving
  of the inverse scattering problem in order to interpret light scattering
  data to determine size, shape, or orientation of the trapped object.
  Experimentally, combining static light scattering techniques with optical
  trapping poses significant engineering challenges due to the space
  constraints in a conventional optical trapping setup. We investigated a
  plausible scenario of detecting scattered light from an optically trapped
  asymmetric particles using a novel, multi-angle, optical-fibre based
  detection scheme, we show how a Bayesian inference-based analysis of the
  data, combined with a neural-network trained on data simulated to mimic
  light scattering detection signals in such scenarios, can be used for
  solving the inverse light scattering problem and characterising colloidal
  trapped entities. To demonstrate the method, we discuss its application to
  measuring the instantaneous orientations of a trapped asymmetric microsphere
  dimer and determine the minimum number of detectors required for a reliable
  estimation in the presence of signal noise. This approach can be extended to
  determine any characteristics of the trapped microstructure that influence
  the light scattering pattern, including size and shape of colloidal objects. 
\end{abstract}

@@

\section{Introduction}
\label{sec:Intro}
Since their invention in the late 1980s, optical tweezers have found application in experiments ranging from single molecule biophysics \cite{Bustamante2021Biophysics} to testing the fundamental assumptions of quantum mechanics \cite{yin2013large}, thanks to the Brownian dynamics of colloidal systems to the tweezer can transduce and detect forces down to the order of a few pico-newtons. Going beyond forces, further structural, dynamic and chemical characterisation of complex trapped entities could provide useful information, as demonstrated in areas such as metrology \cite{arita2020coherent} and colloidal science \cite{burns1990optical}. Spectroscopic techniques such as Raman scattering \cite{gupta2014raman} have been used for chemical characterisation of trapped objects, while dynamical characterisation has been demonstrated using data from tweezer's Quadrant Photo Detector (QPD) by following the centre-of-mass Brownian motion of the trapped entity \cite{friedrich2012tuning} and measuring rotation of the centre-of-mass \cite{yifat2021facile}. A recent work aimed at characterising trapped entities demonstrated how neural networks can be trained to distinguish between optically trapped micro-beads of different size and material by means of a principal component analysis of the forward scattered light detected using a QPD \cite{Carvalho_2023}. A more direct, albeit cumbersome attempt at detecting scattered light from trapped biological cells also was attempted \cite{Watson_2023} where the experimental cuvette was placed inside an elliptical mirror that directed light scattered from the trapped biological-cell onto a photodetector via a rotating aperture that helped select the scattering-angle. Thus, past studies on optical trapping have focused on either on particle trapping to study trapping dynamics, or on the characterisation of particles with relatively simple complex trapping dynamics.

@@

\begin{figure} [h]
\centering
\begin{subfigure}{0.45\textwidth}
	\subcaption{}
	\includegraphics[width=\textwidth, height=0.25\textheight]{./Images/fig1a.png}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
	\subcaption{}
	\includegraphics[width=\textwidth, height=0.25\textheight]{./Images/fig1b.png}
\end{subfigure}
\caption{\label{fig:setup}
  %
  Proposed experimental set up for scattering measurements from an object in an optical trap. The probe beam for scattering measurements is incident perpendicular to the trapping laser propagation direction. a) Side view. b) Top view. Note that three of the detector fibres are co-planar with the incident probe beam, while the fourth detector is placed out of the plane (see Sec~\ref{sec:detectors}).
%
}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig2a.png}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig2b.png}
	\end{subfigure}
	\caption{(a)Example dimer in orientation $\bar{\bf s}$, (b) 30 Reference orientations represented by vectors pointing from [0,0,0] to each point}
	\label{fig:dimer}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.4\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig3a.png}
	\end{subfigure}
	\begin{subfigure}{0.4\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig3b.png}
	\end{subfigure}
	\caption{(a) Distribution of orientation vectors and (b) their respective scattering signals. Points are coloured according to their distance from the centre of each cluster (red points centred around [$0.00, 0.00, 1.00$], blue points centred at [$0.71, 0.00, 0.71$])}
	\label{fig:mixing}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig4a.png}
	\end{subfigure}
	\begin{subfigure}{0.4\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig4b.png}
	\end{subfigure}
	\caption{Expected scattered signals from reference orientations -see fig~\ref{fig:dimer} - when: (a) all three detectors are in the X-Y plane, (b) when 1 detector is raised out of the X-Y plane.}
	\label{fig:detectors}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{./Images/fig8a.png}
\caption{\label{fig:biased}
%
Estimation of dimer orientation with $p(\hat{\bf n}_\alpha)$ defined
by Eq~\eqref{eq:boltz}.  Blue line denotes the best result we can
achieve, orange line denotes the result provided by eq~\ref{eq:bayes}.
Dotted black line is the instantaneous orientation $\hat{\bf s}$ (see Section~\ref{sec:Bayes}).
  %
}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width =\textwidth]{./Images/fig7a.png}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig7b.png}
	\end{subfigure}
	\caption{Simulation results of: (a) the dimer's orientation vector with time, (b) the dimer's [x,y,z] position with time.}
	\label{fig:motion}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.33\textwidth}
			\subcaption{}
			\includegraphics[width =\textwidth]{./Images/fig8a.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig8b.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig8c.png}
	\end{subfigure}
	\caption{Model estimates of orientation when neural net has been trained on dimer of size ratio: (a) 1:2 $[F(K_l)=9.456]$, (b) 1:2.05 $[F(K_l)=1.324]$, (c) 1:1.95 $[F(K_l)=1.325]$ ($n_{refs} = 30$)}
	\label{fig:size}
\end{figure}
As can be seen from Fig~\ref{fig:size}  even the slightest change in size ratio makes a very significant difference to the performance of our model. This amounts to just over $100 \ nm$ in the dimer's overall size, yet results in our model being correct from over 90 \% of the time to now as low as 30 \%. This highlights the importance of correctly sizing trapped entities before performing any in depth analysis of the scattering pattern, as even the slightest deviation can have a serious impact. We addressed this by increasing the number of available reference orientations from 30 to 126 (following the same procedure as given by \cite{Rey2006} to evenly space out the coordinates) and increasing the weighting factor in Eq~\ref{eq:boltz}. While this didn't have a significant improvement on the overall accuracy of the model, in the worst case having a slight increase from 30.5 \% to 40.3 \%, it did help to significantly reduce the magnitude between our model's estimations and the dimer's motion as seen below in Fig~\ref{fig:refs}.

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width =\textwidth]{./Images/fig9a.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig9b.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig9c.png}
	\end{subfigure}
	\caption{Model estimates of orientation when neural net has been trained on dimer of size ratio: (a) 1:2 $[F(K_l)=11.756]$, (b) 1:2.05 $[F(K_l)=1.233]$, (c) 1:1.95 $[F(K_l)=2.128]$, ($n_{refs} = 126$)}
	\label{fig:refs}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig10a.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig10b.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig10c.png}
	\end{subfigure}
	\caption{Model prediction for signal error of (a) $1\%$ ~  $[F(K_l)=7.246]$, (b) $15\%$ $[F(K_l)=0.511]$, and (c) $25\%$ ~  $[F(K_l)=0.536]$.}
	\label{fig:epsilon}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig11a.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig11b.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{./Images/fig11c.png}
	\end{subfigure}
	\caption{Model prediction for signal error of (a) $1\%$ $[F(K_l)=4.823]$,  (b) $15\%$ $[F(K_l)=1.494]$, and (c) $25\%$ $[F(K_l)=0.882]$, time averaged over $1\,{\rm ms}$}
	\label{fig:time average}
\end{figure}
This resulted in a reduction in the overall signal noise and provided a higher degree of accuracy for our model. There appears to be no clear correlation between the length over which we time average and the performance of our model. Time averaging over every 0.05s resulted in a drastically worse performance; this is due to the fact that over longer time periods there is greater uncertainty regarding how the dimer's orientation has changed, thus tracking the instantaneous orientation becomes harder for the neural network. Fortunately, time averaging even over $1\,{\rm ms}$ seems to provide a satisfactory estimation of the dimer's angular dynamics within the optical trap.

@@

We have developed a method for measuring the dynamics of an optically-trapped colloidal objects based purely on measurements of the object's light scattering at a small number of detection angles. We demonstrate the method using the orientation of an asymmetric dimer as the dynamic variable and object of interest respectively, but in principle the model can be applied to any characteristic that impacts the light scattering pattern produced by a trapped entity such as size and shape. The MSTM package is a flexible tool for calculating the light scattering of complex objects using a representation of the object as a set of micro-particles, enabling training of a neural network to enable categorisation of the mapping between scattering and trapped object characteristics. By taking account of the physically realistic behaviour of the trapped object and the characteristics of the trap (which impact the dynamics of the object), the Bayesian inference method can be re ned to provide a reliable estimation of object characteristics of interest, even in the presence of measurement noise. Fundamentally, the inverse scattering problem is difficult to solve, since the mapping between object characteristics and scattering can be highly complex. We determined the minimum number of detectors required for a reliable estimation in the presence of measurement noise; furthermore, we demonstrated that the arrangement of these detectors is critical for a reliable estimation of an objects orientation. However, Bayesian inference based on neural network estimation of the mapping provides a powerful method for practical applications, extending the use of optical trapping beyond measuring microscopic force response toward detailed structural and dynamic information about complex trapped entities.

@@

\newpage
\appendix
\onecolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix}
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\begin{table}[h]
	\begin{center}
		\caption{\label{tab:A1}
		%
		Reference Orientations vector components, for $n_{refs} = 30 \ ^*$}
		\begin{tabularx}{0.9\textwidth}{
				| >{\centering\arraybackslash}X
				| >{\centering\arraybackslash}X
				| >{\centering\arraybackslash}X
				| >{\centering\arraybackslash}X | }
			\hline\hline
			$\alpha$ & $\hat{\bf n}_{\alpha,\ x}$ &  $\hat{\bf n}_{\alpha,\ y}$ &  $\hat{\bf n}_{\alpha,\ z}$ 
			\\ \hline
			$1$ & $0.2958759$ & $0.2958759$ & $0.9082483$ \\
			$2$ & $0.9082483$ & $0.2958759$ & $0.2958759$ \\
			$3$ & $0.2958759$ & $0.9082483$ & $0.2958759$ \\
			$4$ & $0.2958759$ & $0.2958759$ & $-0.9082483$ \\
			$5$ & $0.9082483$ & $0.2958759$ & $-0.2958759$ \\
			$6$ & $0.2958759$ & $0.9082483$ & $-0.2958759$ \\
			$7$ & $0.2958759$ & $-0.2958759$ & $0.9082483$ \\
			$8$ & $0.9082483$ & $-0.2958759$ & $0.2958759$ \\
			$9$ & $0.2958759$ & $-0.9082483$ & $0.2958759$ \\
			$10$ & $0.2958759$ & $-0.2958759$ & $-0.9082483$ \\
			$11$ & $0.9082483$ & $-0.2958759$ & $-0.2958759$ \\
			$12$ & $0.2958759$ & $-0.9082483$ & $-0.2958759$ \\
			$13$ & $-0.2958759$ & $0.2958759$ & $0.9082483$ \\
			$14$ & $-0.9082483$ & $0.2958759$ & $0.2958759$ \\
			$15$ & $-0.2958759$ & $0.9082483$ & $0.2958759$ \\
			$16$ & $-0.2958759$ & $0.2958759$ & $-0.9082483$ \\
			$17$ & $-0.9082483$ & $0.2958759$ & $-0.2958759$ \\
			$18$ & $-0.2958759$ & $0.9082483$ & $-0.2958759$ \\
			$19$ & $-0.2958759$ & $-0.2958759$ & $0.9082483$ \\
			$20$ & $-0.9082483$ & $-0.2958759$ & $0.2958759$ \\
			$21$ & $-0.2958759$ & $-0.9082483$ & $0.2958759$ \\
			$22$ & $-0.2958759$ & $-0.2958759$ & $-0.9082483$ \\
			$23$ & $-0.9082483$ & $-0.2958759$ & $-0.2958759$ \\
			$24$ & $-0.2958759$ & $-0.9082483$ & $-0.2958759$ \\
			$25$ & $1.0000$ & $0.0000$ & $0.0000$ \\
			$26$ & $0.0000$ & $1.0000$ & $0.0000$ \\
			$27$ & $0.0000$ & $0.0000$ & $1.0000$ \\
			$28$ & $-1.000$ & $0.0000$ & $0.0000$ \\
			$29$ & $0.0000$ & $-1.000$ & $0.0000$ \\
			$30$ & $0.0000$ & $0.0000$ & $-1.000$ \\

>>>>

\documentclass[12pt]{spieman}

\usepackage{csvsimple}
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{wrapfig}
\usepackage{geometry}
\usepackage{fancyref}
\usepackage{lineno}
\usepackage{color}
\usepackage{nomencl}
\usepackage{tabularx}
\usepackage{graphicx}
\makenomenclature
\renewcommand{\nomlabel}[1]{\hfil #1\hfil}
\linenumbers

@@

\author[a*]{Daniel Maciver}
\author[a]{Praveen Parthasarathi}
\author[a]{Leo Lue} 
\author[a]{Jan Sefcik}
\author[a]{Mark Haw}

\affil[a]{Department of Chemical Engineering,
	University of Strathclyde, 75 Montrose Street, Glasgow,
	G1 1XL, Scotland}

\begin{document}
	\maketitle
\begin{abstract}
  % \justifying
  %
  Optical trapping is a well understood method for transduction and detection
  of forces on trapped colloidal particles, these trapped entities can be
  further characterised using light-scattering, posing a two-fold challenge:
  one experimental, concerning the optimal arrangement of detectors to gather
  data and minimise signal noise, and the other theoretical, involving solving
  of the inverse scattering problem in order to interpret light scattering
  data to determine size, shape, or orientation of the trapped object.
  Experimentally, combining static light scattering techniques with optical
  trapping poses significant engineering challenges due to the space
  constraints in a conventional optical trapping setup. We investigated a
  plausible scenario of detecting scattered light from an optically trapped
  asymmetric particles using a novel, multi-angle, optical-fibre based
  detection scheme, we show how a Bayesian inference-based analysis of the
  data, combined with a neural-network trained on data simulated to mimic
  light scattering detection signals in such scenarios, can be used for
  solving the inverse light scattering problem and characterising colloidal
  trapped entities. To demonstrate the method, we discuss its application to
  measuring the instantaneous orientations of a trapped asymmetric microsphere
  dimer and determine the minimum number of detectors required for a reliable
  estimation in the presence of signal noise. This approach can be extended to
  determine any characteristics of the trapped microstructure that influence
  the light scattering pattern, including size and shape of colloidal objects. 
\end{abstract}

@@

\section{Introduction}
\begin{spacing}{1.5}

\label{sec:Intro}
Since their invention in the late 1980s, optical tweezers have found application in experiments ranging from single molecule biophysics \cite{Bustamante2021Biophysics} to testing the fundamental assumptions of quantum mechanics \cite{yin2013large}, thanks to the Brownian dynamics of colloidal systems to the tweezer can transduce and detect forces down to the order of a few pico-newtons. Going beyond forces, further structural, dynamic and chemical characterisation of complex trapped entities could provide useful information, as demonstrated in areas such as metrology \cite{arita2020coherent} and colloidal science \cite{burns1990optical}. Spectroscopic techniques such as Raman scattering \cite{gupta2014raman} have been used for chemical characterisation of trapped objects, while dynamical characterisation has been demonstrated using data from tweezer's Quadrant Photo Detector (QPD) by following the centre-of-mass Brownian motion of the trapped entity \cite{friedrich2012tuning} and measuring rotation of the centre-of-mass \cite{yifat2021facile}. A recent work aimed at characterising trapped entities demonstrated how neural networks can be trained to distinguish between optically trapped micro-beads of different size and material by means of a principal component analysis of the forward scattered light detected using a QPD \cite{Carvalho_2023}. A more direct, albeit cumbersome attempt at detecting scattered light from trapped biological cells also was attempted \cite{Watson_2023} where the experimental cuvette was placed inside an elliptical mirror that directed light scattered from the trapped biological-cell onto a photodetector via a rotating aperture that helped select the scattering-angle. Thus, past studies on optical trapping have focused on either on particle trapping to study trapping dynamics, or on the characterisation of particles with relatively simple complex trapping dynamics.

@@

\begin{figure} [h]
\centering
\begin{subfigure}{0.45\textwidth}
	\includegraphics[width=5.5cm, height=5.5cm]{./Images/fig1a.png}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
	\includegraphics[width=5.5cm, height=5.5cm]{./Images/fig1b.png}
\end{subfigure}
\caption{\label{fig:setup}
  %
  Proposed experimental set up for scattering measurements from an object in an optical trap. The probe beam for scattering measurements is incident perpendicular to the trapping laser propagation direction. a) Side view. b) Top view. Note that three of the detector fibres are co-planar with the incident probe beam, while the fourth detector is placed out of the plane (see Sec~\ref{sec:detectors}).
%
}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig2a.png}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig2b.png}
	\end{subfigure}
	\caption{(a)Example dimer in orientation $\bar{\bf s}$, (b) 30 Reference orientations represented by vectors pointing from [0,0,0] to each point}
	\label{fig:dimer}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.4\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig3a.png}
	\end{subfigure}
	\begin{subfigure}{0.4\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig3b.png}
	\end{subfigure}
	\caption{(a) Distribution of orientation vectors and (b) their respective scattering signals. Points are coloured according to their distance from the centre of each cluster (red points centred around [$0.00, 0.00, 1.00$], blue points centred at [$0.71, 0.00, 0.71$])}
	\label{fig:mixing}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig4a.png}
	\end{subfigure}
	\begin{subfigure}{0.4\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig4b.png}
	\end{subfigure}
	\caption{Expected scattered signals from reference orientations -see fig~\ref{fig:dimer} - when: (a) all three detectors are in the X-Y plane, (b) when 1 detector is raised out of the X-Y plane.}
	\label{fig:detectors}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=5.5cm]{./Images/fig8a.png}
\caption{\label{fig:biased}
%
Estimation of dimer orientation with $p(\hat{\bf n}_\alpha)$ defined
by Eq~\eqref{eq:boltz}.  Blue line denotes the best result we can
achieve, orange line denotes the result provided by eq~\ref{eq:bayes}.
Dotted black line is the instantaneous orientation $\hat{\bf s}$ (see Section~\ref{sec:Bayes}).
  %
}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width =5.5cm]{./Images/fig7a.png}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig7b.png}
	\end{subfigure}
	\caption{Simulation results of: (a) the dimer's orientation vector with time, (b) the dimer's [x,y,z] position with time.}
	\label{fig:motion}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.33\textwidth}
			\subcaption{}
			\includegraphics[width =5.5cm]{./Images/fig8a.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig8b.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig8c.png}
	\end{subfigure}
	\caption{Model estimates of orientation when neural net has been trained on dimer of size ratio: (a) 1:2 $[F(K_l)=9.456]$, (b) 1:2.05 $[F(K_l)=1.324]$, (c) 1:1.95 $[F(K_l)=1.325]$ ($n_{refs} = 30$)}
	\label{fig:size}
\end{figure}
As can be seen from Fig~\ref{fig:size}  even the slightest change in size ratio makes a very significant difference to the performance of our model. This amounts to just over $100 \ nm$ in the dimer's overall size, yet results in our model being correct from over 90 \% of the time to now as low as 30 \%. This highlights the importance of correctly sizing trapped entities before performing any in depth analysis of the scattering pattern, as even the slightest deviation can have a serious impact. We addressed this by increasing the number of available reference orientations from 30 to 126 (following the same procedure as given by \cite{Rey2006} to evenly space out the coordinates) and increasing the weighting factor in Eq~\ref{eq:boltz}. While this didn't have a significant improvement on the overall accuracy of the model, in the worst case having a slight increase from 30.5 \% to 40.3 \%, it did help to significantly reduce the magnitude between our model's estimations and the dimer's motion as seen below in Fig~\ref{fig:refs}.

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width =5.5cm]{./Images/fig9a.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig9b.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig9c.png}
	\end{subfigure}
	\caption{Model estimates of orientation when neural net has been trained on dimer of size ratio: (a) 1:2 $[F(K_l)=11.756]$, (b) 1:2.05 $[F(K_l)=1.233]$, (c) 1:1.95 $[F(K_l)=2.128]$, ($n_{refs} = 126$)}
	\label{fig:refs}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig10a.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig10b.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig10c.png}
	\end{subfigure}
	\caption{Model prediction for signal error of (a) $1\%$ ~  $[F(K_l)=7.246]$, (b) $15\%$ $[F(K_l)=0.511]$, and (c) $25\%$ ~  $[F(K_l)=0.536]$.}
	\label{fig:epsilon}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig11a.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig11b.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=5.5cm]{./Images/fig11c.png}
	\end{subfigure}
	\caption{Model prediction for signal error of (a) $1\%$ $[F(K_l)=4.823]$,  (b) $15\%$ $[F(K_l)=1.494]$, and (c) $25\%$ $[F(K_l)=0.882]$, time averaged over $1\,{\rm ms}$}
	\label{fig:time average}
\end{figure}
This resulted in a reduction in the overall signal noise and provided a higher degree of accuracy for our model. There appears to be no clear correlation between the length over which we time average and the performance of our model. Time averaging over every 0.05s resulted in a drastically worse performance; this is due to the fact that over longer time periods there is greater uncertainty regarding how the dimer's orientation has changed, thus tracking the instantaneous orientation becomes harder for the neural network. Fortunately, time averaging even over $1\,{\rm ms}$ seems to provide a satisfactory estimation of the dimer's angular dynamics within the optical trap.

@@

We have developed a method for measuring the dynamics of an optically-trapped colloidal objects based purely on measurements of the object's light scattering at a small number of detection angles. We demonstrate the method using the orientation of an asymmetric dimer as the dynamic variable and object of interest respectively, but in principle the model can be applied to any characteristic that impacts the light scattering pattern produced by a trapped entity such as size and shape. The MSTM package is a flexible tool for calculating the light scattering of complex objects using a representation of the object as a set of micro-particles, enabling training of a neural network to enable categorisation of the mapping between scattering and trapped object characteristics. By taking account of the physically realistic behaviour of the trapped object and the characteristics of the trap (which impact the dynamics of the object), the Bayesian inference method can be re ned to provide a reliable estimation of object characteristics of interest, even in the presence of measurement noise. Fundamentally, the inverse scattering problem is difficult to solve, since the mapping between object characteristics and scattering can be highly complex. We determined the minimum number of detectors required for a reliable estimation in the presence of measurement noise; furthermore, we demonstrated that the arrangement of these detectors is critical for a reliable estimation of an objects orientation. However, Bayesian inference based on neural network estimation of the mapping provides a powerful method for practical applications, extending the use of optical trapping beyond measuring microscopic force response toward detailed structural and dynamic information about complex trapped entities. 
\end{spacing}

@@

\newpage
\appendix
\onecolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix}
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\begin{table}[h]
	\begin{center}
		\caption{\label{tab:A1}
		%
		Reference Orientations vector components, for $n_{refs} = 30 \ ^*$}
		\begin{tabularx}{0.7\textwidth}{
				| >{\centering\arraybackslash}X
				| >{\centering\arraybackslash}X
				| >{\centering\arraybackslash}X
				| >{\centering\arraybackslash}X | }
			\hline\hline
			$\alpha$ & $\hat{\bf n}_{\alpha,\ x}$ &  $\hat{\bf n}_{\alpha,\ y}$ &  $\hat{\bf n}_{\alpha,\ z}$ 
			\\ \hline
			$1$ & $0.2958759$ & $0.2958759$ & $0.9082483$ \\
			$2$ & $0.9082483$ & $0.2958759$ & $0.2958759$ \\
			$3$ & $0.2958759$ & $0.9082483$ & $0.2958759$ \\
			$4$ & $0.2958759$ & $0.2958759$ & $-0.9082483$ \\
			$5$ & $0.9082483$ & $0.2958759$ & $-0.2958759$ \\
			$6$ & $0.2958759$ & $0.9082483$ & $-0.2958759$ \\
			$7$ & $0.2958759$ & $-0.2958759$ & $0.9082483$ \\
			$8$ & $0.9082483$ & $-0.2958759$ & $0.2958759$ \\
			$9$ & $0.2958759$ & $-0.9082483$ & $0.2958759$ \\
			$10$ & $0.2958759$ & $-0.2958759$ & $-0.9082483$ \\
			$11$ & $0.9082483$ & $-0.2958759$ & $-0.2958759$ \\
			$12$ & $0.2958759$ & $-0.9082483$ & $-0.2958759$ \\
			$13$ & $-0.2958759$ & $0.2958759$ & $0.9082483$ \\
			$14$ & $-0.9082483$ & $0.2958759$ & $0.2958759$ \\
			$15$ & $-0.2958759$ & $0.9082483$ & $0.2958759$ \\
			$16$ & $-0.2958759$ & $0.2958759$ & $-0.9082483$ \\
			$17$ & $-0.9082483$ & $0.2958759$ & $-0.2958759$ \\
			$18$ & $-0.2958759$ & $0.9082483$ & $-0.2958759$ \\
			$19$ & $-0.2958759$ & $-0.2958759$ & $0.9082483$ \\
			$20$ & $-0.9082483$ & $-0.2958759$ & $0.2958759$ \\
			$21$ & $-0.2958759$ & $-0.9082483$ & $0.2958759$ \\
			$22$ & $-0.2958759$ & $-0.2958759$ & $-0.9082483$ \\
			$23$ & $-0.9082483$ & $-0.2958759$ & $-0.2958759$ \\
			$24$ & $-0.2958759$ & $-0.9082483$ & $-0.2958759$ \\
			$25$ & $1.0000$ & $0.0000$ & $0.0000$ \\
			$26$ & $0.0000$ & $1.0000$ & $0.0000$ \\
			$27$ & $0.0000$ & $0.0000$ & $1.0000$ \\
			$28$ & $-1.000$ & $0.0000$ & $0.0000$ \\
			$29$ & $0.0000$ & $-1.000$ & $0.0000$ \\
			$30$ & $0.0000$ & $0.0000$ & $-1.000$ \\
